Local Spectral Clustering of Density Upper Level Sets

### 2020-11-29 jmlr/revision/local_spectral_density_clustering_jmlr_revision.tex
test commit
Improved constants in upper bounds of normalized cut and mixing time.

%%% Sets
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Asig}{\Aset_{\sigma}}
\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Asigr}{\Aset_{\sigma,\sigma + r}}
\newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}

@@

%%% Tilde notation for quantities over the expansion set 
\newcommand{\wn}{\widetilde{n}}
\newcommand{\wX}{\widetilde{\Xbf}}
\newcommand{\wx}{\widetilde{x}}
\newcommand{\wz}{\widetilde{z}}
\newcommand{\wbz}{\widetilde{\bf{z}}}
\newcommand{\wu}{\widetilde{u}}
\newcommand{\wPbb}{\widetilde{\Pbb}}
\newcommand{\wf}{\widetilde{f}}
\newcommand{\wDbf}{\widetilde{\Dbf}}
\newcommand{\piwt}{\widetilde{\pi}}

\newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}

@@

@@

@@

\begin{theorem}
  \label{thm: conductance_upper_bound}
  Fix $\lambda,\sigma>0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies    
  Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and   
  \ref{asmp: bounded_volume}. Then
  \begin{equation}
    \label{eqn: conductance_additive_error_bound}
    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}},
  \end{equation}
  with probability at least $1 - 3\exp\set{-b n}$. 
\end{theorem}

@@

\begin{theorem}
  \label{thm: mixing_time_upper_bound}
  Fix $\lambda, \sigma > 0$, and assume \smash{$\Cset \in \Cbb_f(\lambda)$} 
  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
  Also assume that \smash{$0 < r \leq \sigma/(2\sqrt{d})$}. Then for any
  $$
  n \geq b_1 (\log n)^{\max\{\frac{3}{d},1\}},
  $$
  the mixing time satisfies
  \begin{equation} 
    \label{eqn: mixing_time_upper_bound}
    \tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 
      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{
        \Lambda_{\sigma}}{\lambda_{\sigma}^2 r}\right) + c_3, 
  \end{equation}
  with probability at least $1 - b_2/n$.
\end{theorem}
The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
analogous mixing time bounds developed for a continuous-space ``ball walk'' over
convex sets. To the best of our knowledge, our result is the first bound on the
mixing time of random walks over neighborhood graphs that is independent of $n$,
the number of vertices.

@@

\subsection{Comparison with previous upper bound}

@@

The proof of this theorem follows essentially from two technical Lemmas. 
Lemma~\ref{lem:ball_bounds_in_probability} relates the terms in the numerator and denominator of $\Phi_{n,r}(\Csig[\Xbf])$ to their expected values. We restate the conclusions of this Lemma: for any $\delta > 0$,
\begin{align}
\frac{\cut_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq (1 + \delta)\cut_{\Pbb,r}(\Csig) &, \quad \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \geq (1 - \delta)\vol_{\Pbb,r}(\Csig) \nonumber \\ \frac{\vol_{n,r}((\Rd \setminus \Csig)[\Xbf])}{2{n \choose 2}}& \geq (1 - \delta)\vol_{\Pbb,r}(\Rd \setminus \Csig) \label{eqn: conductance_upper_bound_pf1}
\end{align}
with probability at least 
\begin{align*}
1 - & \exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Rd\setminus \Csig))^2} \\
& \geq 1 - 3\exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2}.
\end{align*} 
We note that as a consequence of~\ref{asmp: bounded_volume} we have that $\vol_{\Pbb,r}(\Rd \setminus \Csig)  \geq \vol_{\Pbb,r}(\Csig)$, so it will suffice to lower bound $\vol_{\Pbb,r}(\Csig)$ (since a lower bound for $\vol_{\Pbb,r}(\Rd \setminus \Csig)$ follows).
The following result provides upper and lower bounds on the expected values $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$ respectively:
\begin{lemma}
	\label{lem: expected_density_cut}\label{lem: expected_density_volume}
	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
	\begin{align}
	\cut_{\Pbb,r}(\Csig) &\leq \frac{4 d \nu_d r^{d+1} \lambda}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
	\vol_{\Pbb,r}(\Csig) &\geq \frac{12}{25} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
	\end{align}
\end{lemma}
Taking Lemma~\ref{lem: expected_density_cut} and \eqref{eqn: conductance_upper_bound_pf1} as given we can now complete the proof of the theorem. We lower bound $\Phi_{n,r}(\Csig[\Xbf])$ as follows:
\begin{equation*}
\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{25(1 + \delta)d \nu_d r \lambda \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{3(1 - \delta) \sigma \lambda_{\sigma}^2}.
\end{equation*}
Plugging in $\delta = \frac{1}{2}$, the theorem is satisfied by choosing constants $c_1 = 50$ and $b = \frac{1}{4}(\cut_{\Pbb,r}(\Csig))^2$.

\subsection{Proof of Lemma~\ref{lem: expected_density_cut}}
We write $\Pbb(\Aset) = \int_{\Aset} f(x) dx$ for measurable $\Aset \subseteq \Rd$.
We 
let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}. 
Our goal will be to upper bound $\cut_{\Pbb,r}(\Csig)$ by a term that depends on the probability mass $\Pbb(\Csigr)$, 
and the bulk of our technical effort will be devoted to showing the following upper bound on $\Pbb(\Csigr)$:
%Lemma \ref{lem: expected_number_boundary_points} involves the bulk of the technical effort required to prove Theorem \ref{thm: conductance_upper_bound}; it will be necessary to bound the expected cut size of $\Csig[\Xbf]$ in $G_{n,r}$. 
\begin{lemma}
	\label{lem: expected_number_boundary_points}
	Under the conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
	\begin{equation*}
	\Pbb(\Csigr) \leq \frac{2dr}{\sigma} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
	\end{equation*}	
\end{lemma}
\noindent Define the \emph{uniform local conductance} $\ell_{\nu,r}(u)$ to be
\begin{equation*}
\ell_{\nu,r}(u) = \nu\bigl(\Csig \cap B(u,r)\bigr).
\end{equation*}
In order to lower bound $\vol_{\Pbb,r}(\Csig)$ we will show the following lower bound on the uniform local conductance:
\begin{lemma}
	\label{lem: local_conductance}
	Let $u \in \Csig$. Then, for any $0 < r \leq \frac{\sigma}{2\sqrt{d}}$,
	\begin{equation*}
	\ell_{\nu,r}(u) \geq \frac{6}{25} \nu_d r^d.
	\end{equation*}
\end{lemma}
Taking these two results as given we can now prove each of the two claims~\eqref{eqn:claim_one} and~\eqref{eqn:claim_two} in turn.
\paragraph{Proof of Claim~\eqref{eqn:claim_one}: } For each $i,j$ such that $i \neq j$, we can write 
\begin{equation*}
\cut_{\Pbb,r}(\Csig) =  \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r).
\end{equation*}
Writing this as an integral, we have
\begin{align*}
\cut_{\Pbb,r}(\Csig) & = \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
& = \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
& \leq \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = \nu_d r^d \lambda \Pbb(\Csigr).
\end{align*}
where the inequality follows from \ref{asmp: low_noise_density}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$. Then, upper bounding the integral using Lemma \ref{lem: expected_number_boundary_points} gives the final result.

%\subsection{Proof of Lemma~\ref{Z}}
\paragraph{Proof of Claim~\eqref{eqn:claim_two}: }  For each $i,j$ such that $i \neq j$, we can write 
\begin{equation*}
\vol_{\Pbb,r}(\Csig) = \Pbb(x_i \in \Csig, x_j \in B(x_i,r))
\end{equation*}
Writing this as an integral, we have
\begin{align*}
\vol_{\Pbb,r}(\Csig) & = 2 \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
& \geq 2 \int_{\Csig} f(x) \Pbb(B(x,r) \cap \Csig) \dx
\end{align*}
whence the claim then follows by Lemma \ref{lem: local_conductance}.
It remains to prove Lemmas~\ref{lem: expected_number_boundary_points} and~\ref{lem: local_conductance}, and we turn our attention to this next.
\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
The proof of this Lemma relies on certain volume estimates whose statement and proof we defer to Appendix~\ref{sec: volume_estimates}.
	We partition $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
	\begin{equation*}
	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k},
	\end{equation*}
	where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
	\begin{equation}
	\label{eqn: partition_ub}
	\Pbb(\Csigr) = \int_{\Csigr} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
	\end{equation}
	Assumptions~\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
	\begin{equation*}
	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma},
	\end{equation*}
	and writing
	\begin{equation*}
	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
	\end{equation*}
	we have
	\begin{align}
	\label{eqn: telescoping_sum}
	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
	& = \underbrace{\sum_{i = 1}^{k} 
	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
	\end{align}
	where the second equality comes from rearranging terms in the sum.

	% AJG 5/14/19: This argument makes sense, correct?
	We first consider the term $\Sigma_k$. $\Cset$ has finite diameter by Assumption~\ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$. Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero). As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
	\begin{equation}
	\label{eqn: slice_volume_bound}
	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
	\end{equation}
	which in turn gives
	\begin{align}
	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
	\end{align}
	The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
	\begin{align}
	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
	\end{align}
	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(2d)$.

>>>>

%%% Sets
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Aset}{\mathcal{A}}
\newcommand{\Asig}{\Aset_{\sigma}}
\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Asigr}{\Aset_{\sigma,\sigma + r}}
\newcommand{\Csigr}{\Cset_{\sigma,\sigma + r}}

@@

%%% Tilde notation for quantities over the expansion set 
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wn}{\widetilde{n}}
\newcommand{\wX}{\widetilde{\Xbf}}
\newcommand{\wx}{\widetilde{x}}
\newcommand{\wz}{\widetilde{z}}
\newcommand{\wbz}{\widetilde{\bf{z}}}
\newcommand{\wu}{\widetilde{u}}
\newcommand{\wPbb}{\widetilde{\Pbb}}
\newcommand{\wf}{\widetilde{f}}
\newcommand{\wDbf}{\widetilde{\Dbf}}
\newcommand{\piwt}{\widetilde{\pi}}

\newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}
\newcommand{\ag}[1]{\textcolor{red}{#1}}

@@

\textcolor{red}{Need to fix this definition: (1) the universal constants are not given in the Theorem statements, and (2) the definition of $\tau_u(\mc{C})$ has changed.}

@@

\textcolor{red}{Need to fix this Theorem.}

@@

\begin{theorem}
  \label{thm: conductance_upper_bound}
  Fix $\lambda,\sigma>0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies    
  Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density}, and   
  \ref{asmp: bounded_volume}. Then for any $\delta \in (0,1/2)$, it holds that
  \begin{equation}
    \label{eqn: conductance_additive_error_bound}
    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq (1 + 4\delta) c_1\frac{d}{\sigma}
    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}},
  \end{equation}
  with probability at least $1 - 3\exp\set{-b n \delta^2}$. 
\end{theorem}

@@

\begin{theorem}
  \label{thm: mixing_time_upper_bound}
  Fix $\lambda, \sigma > 0$, and assume \smash{$\Cset \in \Cbb_f(\lambda)$} 
  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}.
  Also assume that \smash{$0 < r \leq \sigma/(4d)$}. Then for any \smash{$\delta \in \bigl(0,1/(8 + 16/d)\bigr)$}, and any
  $$
  n \geq b_1 \cdot (1 + 4\delta) \cdot 
  \begin{cases*}
  \log(n)^{3/2},& ~~\textrm{if $d = 2$,} \\
  \log(n),& ~~\textrm{if $d \neq 2$}
  \end{cases*}
  $$
  the mixing time satisfies
  \begin{align} 
    \label{eqn: mixing_time_upper_bound}
    \tau_{\infty}\bigl(G_{n,r}[\Csig[\Xbf]]\bigr) & \leq (1 + 40\delta) c_2 \frac{\Lambda_{\sigma}^4 d^3 
      \rho^2 L^2}{\lambda_{\sigma}^4 r^2} \log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr)\log\Bigl(c_5^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + \\
  &~~c_3\biggl((1 + 32\delta)d\log\Bigl(c_4^{1/d}\frac{\Lambda_{\sigma}^{2/d}L\rho}{\lambda_{\sigma}^{2/d}\sigma}\Bigr) + 1\biggr), 
  \end{align}
  with probability at least $1 - b_5/n - 4n\exp\{-\delta^2 b_2 n\}$.
\end{theorem}
The proof of Theorem \ref{thm: mixing_time_upper_bound} relies heavily on
analogous mixing time bounds developed for a continuous-space ``ball walk'' over
convex sets. To the best of our knowledge, our result is the first bound on the
mixing time of random walks over neighborhood graphs that is independent of $n$,
the number of vertices.

@@

\subsection{Comparison \ag{between upper and lower bounds}.}

@@

The proof of this theorem follows essentially from two technical Lemmas. 
Lemma~\ref{lem:ball_bounds_in_probability} relates the terms in the numerator and denominator of $\Phi_{n,r}(\Csig[\Xbf])$ to their expected values. We restate the conclusions of this Lemma: for any $\delta > 0$,
\begin{align}
\frac{\cut_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \leq (1 + \delta)\cut_{\Pbb,r}(\Csig) &, \quad \frac{\vol_{n,r}(\Csig[\Xbf])}{2{n \choose 2}} \geq (1 - \delta)\vol_{\Pbb,r}(\Csig) \nonumber \\ \frac{\vol_{n,r}((\Rd \setminus \Csig)[\Xbf])}{2{n \choose 2}}& \geq (1 - \delta)\vol_{\Pbb,r}(\Rd \setminus \Csig) \label{eqn: conductance_upper_bound_pf1}
\end{align}
with probability at least 
\begin{align*}
1 - & \exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Csig))^2} - \exp\set{-n \delta^2 (\vol_{\Pbb,r}(\Rd\setminus \Csig))^2} \\
& \geq 1 - 3\exp\set{-n \delta^2 (\cut_{\Pbb,r}(\Csig))^2}.
\end{align*} 
We note that as a consequence of~\ref{asmp: bounded_volume} we have that $\vol_{\Pbb,r}(\Rd \setminus \Csig)  \geq \vol_{\Pbb,r}(\Csig)$, so it will suffice to lower bound $\vol_{\Pbb,r}(\Csig)$ (since a lower bound for $\vol_{\Pbb,r}(\Rd \setminus \Csig)$ follows).
The following result provides upper and lower bounds on the expected values $\cut_{\Pbb,r}(\Csig)$ and $\vol_{\Pbb,r}(\Csig)$ respectively:
\begin{lemma}
	\label{lem: expected_density_cut}\label{lem: expected_density_volume}
	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $0 < r \leq \sigma/(2d)$,
	\begin{align}
	\cut_{\Pbb,r}(\Csig) &\leq \frac{ d \nu_d r^{d+1} \lambda}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig), \label{eqn:claim_one} \\
	\vol_{\Pbb,r}(\Csig) &\geq \biggl(1 + \frac{dr}{\sigma - dr}\biggr)^{-1} \lambda_{\sigma}^2 \nu_d r^d \nu(\Csig).\label{eqn:claim_two}
	\end{align}
\end{lemma}
Taking Lemma~\ref{lem: expected_density_cut} and \eqref{eqn: conductance_upper_bound_pf1} as given we can now complete the proof of the theorem. We lower bound $\Phi_{n,r}(\Csig[\Xbf])$ as follows:
\begin{equation*}
\Phi_{n,r}(\Csig[\Xbf]) \leq \frac{(1 + \delta)\cut_{\Pbb,r}(\Csig)}{(1 - \delta)\vol_{\Pbb,r}(\Csig)} \leq \frac{(1 + \delta)}{(1 - \delta)(1 - dr/\sigma)^2}\frac{d \nu_d r \lambda \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right)}{\sigma \lambda_{\sigma}^2}.
\end{equation*}
Noting that $(1 - dr/\sigma)^{-2} \leq 1 + 6dr/\sigma \leq 4$ for all $r \leq \sigma/2d$, the theorem is satisfied by choosing $c_1 = 4$ and $b = (\cut_{\Pbb,r}(\Csig))^2$.

\subsection{Proof of Lemma~\ref{lem: expected_density_cut}}
We write $\Pbb(\Aset) = \int_{\Aset} f(x) dx$ for measurable $\Aset \subseteq \Rd$.
We 
let $\Csigr := \set{x: 0 < \dist(x, \Csig) < r}$, where $\Csig$ is as in Theorem \ref{thm: conductance_upper_bound}. 
Our goal will be to upper bound $\cut_{\Pbb,r}(\Csig)$ by a term that depends on the probability mass $\Pbb(\Csigr)$, 
and the bulk of our technical effort will be devoted to showing the following upper bound on $\Pbb(\Csigr)$:
\begin{lemma}
	\label{lem: expected_number_boundary_points}
	For any $0 < r \leq \sigma/(2d)$, under the conditions of Theorem \ref{thm: conductance_upper_bound} it holds that
	\begin{equation*}
	\Pbb(\Csigr) \leq \frac{dr}{\sigma - dr} \left(\lambda_{\sigma} - c_0\frac{r^{\gamma}}{\gamma + 1}\right) \nu(\Csig)
	\end{equation*}	
\end{lemma}
Taking this result as given we can now prove the claim~\eqref{eqn:claim_one}.
\paragraph{Proof of Claim~\eqref{eqn:claim_one}: } For each $i,j$ such that $i \neq j$, we can write 
\begin{equation*}
\cut_{\Pbb,r}(\Csig) =  \Pbb(x_i \not\in \Csig, x_j \in \Csig, \norm{x_i - x_j} \leq r).
\end{equation*}
Writing this as an integral, we have
\begin{align*}
\cut_{\Pbb,r}(\Csig) & = \int_{\Rd \setminus \Csig} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
& = \int_{\Csigr} f(x) \Pbb\bigl(B(x,r) \cap \Csig\bigr) \dx \\
& \leq \nu_d r^d \lambda  \int_{\Csigr} f(x) \dx = \nu_d r^d \lambda \Pbb(\Csigr).
\end{align*}
where the inequality follows from \ref{asmp: low_noise_density}, which implies $f(x) \leq \lambda$ for $x \in \Csig \setminus \Cset$. Then, upper bounding the integral using Lemma \ref{lem: expected_number_boundary_points} gives the final result.

\paragraph{Proof of Claim~\eqref{eqn:claim_two}: } On the other hand, the proof of Claim~\eqref{eqn:claim_two} follows from relating $\vol_{\Pbb,r}(\Csig)$ to the Lebesgue measure of $\mc{C}_{\sigma - r}$. In particular, since $f(y) \geq \lambda_{\sigma}$ for all $x \in \Csig$, and $B(x,r) \subset \Csig$ for all $x \in \mc{C}_{\sigma - r}$, it follows that
\begin{align*}
\vol_{\Pbb,r}(\Csig) & = \int_{\Csig} f(x) \Pbb(B(x,r)) \dx \\
& \geq \int_{\mc{C}_{\sigma - r}} f(x) \Pbb(B(x,r)) \dx \\
& \geq \lambda_{\sigma}^2 \nu_d r^d \nu(\mc{C}_{\sigma - r}).
\end{align*}
Then, noting that by the triangle inequality $\mc{C}_{\sigma} \subseteq \mc{C}_{\sigma - r} + \sigma B$, applying Lemma~\ref{lem: expansion_volume} (given in Appendix~\ref{sec: volume_estimates}) and the Bernoulli inequality (Lemma~\ref{lem: Taylor_series}) gives
\begin{equation*}
\nu(\Cset_{\sigma}) \leq \nu(\Cset_{\sigma - r} + \sigma B) \leq \biggl(1 + \frac{r}{\sigma - r}\biggr)^d \nu(\Cset_{\sigma - r}) \leq \biggl(1 + \frac{dr}{\sigma - dr}\biggr)\nu(\mc{C}_{\sigma - r}),
\end{equation*}
thus establishing the claim.

It remains to prove Lemma~\ref{lem: expected_number_boundary_points} and we turn our attention to this now.
\subsection{Proof of Lemma~\ref{lem: expected_number_boundary_points}}
We note that the proof of this Lemma relies on certain volume estimates whose statement and proof we defer to Appendix~\ref{sec: volume_estimates}.

We begin by partitioning $\Csigr$ into slices based on distance from $\Csig$ as follows: for $k \in \N$,
	\begin{equation*}
	\mathcal{T}_{i,k} = \set{x \in \Csigr: t_{i,k} < \frac{\dist(x, \Csig)}{r} \leq t_{i+1,k}}, ~~ \Csigr = \bigcup_{i = 0}^{k-1} \mathcal{T}_{i,k},
	\end{equation*}
	where $t_{i,k} = i/k$ for $i = 0, \ldots, k - 1$. As a result, for any $k \in \mathbb{N}$,
	\begin{equation}
	\label{eqn: partition_ub}
	\Pbb(\Csigr) = \int_{\Csigr} f(x) \dx = \sum_{i = 0}^{k-1} \int_{\mathcal{T}_{i,k}} f(x) \dx \leq \sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x).
	\end{equation}
	Assumptions~\ref{asmp: bounded_density} and \ref{asmp: low_noise_density} imply the upper bound
	\begin{equation*}
	\max_{x \in \mathcal{T}_{i,k}} f(x) \leq \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma},
	\end{equation*}
	and writing
	\begin{equation*}
	\nu(\mathcal{T}_{i,k}) = \nu(\Csig + rt_{i+1,k}B) - \nu(\Csig + rt_{i,k}B) =: \nu_{i+1,k} - \nu_{i,k},
	\end{equation*}
	we have
	\begin{align}
	\label{eqn: telescoping_sum}
	\sum_{i = 0}^{k-1} \nu(\mathcal{T}_{i,k}) \max_{x \in \mathcal{T}_{i,k}} f(x) & \leq \sum_{i = 0}^{k-1} \biggl\{ \nu_{i+1,k} - \nu_{i,k} \biggr\} \biggl( \lambda_{\sigma} - c_0(rt_{i,k})^{\gamma} \biggr) \nonumber \\
	& = \underbrace{\sum_{i = 1}^{k} 
	\nu_{i,k} \biggl( \left[\lambda_{\sigma} - c_0(rt_{i-1,k})^{\gamma}\right] -  \left[\lambda_{\sigma} - c_0(rt_{i,k})^{\gamma}\right]\biggr)}_{:= \Sigma_k} + \underbrace{\biggl(\nu_{k,k}\left[\lambda_{\sigma} - c_0r^{\gamma}\right] - \nu_{1,k}\lambda_{\sigma} \biggr)}_{:= \xi}
	\end{align}
	where the second equality comes from rearranging terms in the sum.

	% AJG 5/14/19: This argument makes sense, correct?
	We first consider the term $\Sigma_k$. $\Cset$ has finite diameter by Assumption~\ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$. Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero). As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
	\begin{equation}
	\label{eqn: slice_volume_bound}
	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
	\end{equation}
	which in turn gives
	\begin{align}
	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (\text{substituting}~u_{i,k} := t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
	\end{align}
	The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
	\begin{align}
	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{ d r u^{1/\gamma}}{\sigma - dr}\right) du \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{d r}{(\gamma + 1)(\sigma - dr)}\right). \label{eqn: Sigmak_integral}
	\end{align}
	where $\text{(i)}$ follows from the upper bound in Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma/(2d)$.
